Efficient Compilation of High Level Python Numerical Programs with Pythran

### 2014-08-29 doc/papers/cgo2014/paper.tex
Fix citation

C/C++ have been at the hearth of high performance computing for many years.
Compiler infrasturctures for these languages also have a long history and
implement many optimizations on the control flow graph, basic blocks or
loops~\cite{Aho2006} that limit usage of assembly code to a few hot spots.
Language extensions like OpenMP~\cite{openmp4} provide a convenient parallel
programming model and libraries like Boost.SIMD~\cite{boostsimd} provide good
abstractions for explicit vectorization. Many highly tuned kernels are
available in the form of thid-party libraies like GotoBlas~\cite{gotoblas2008}.

@@

>>>>

C/C++ have been at the hearth of high performance computing for many years.
Compiler infrasturctures for these languages also have a long history and
implement many optimizations on the control flow graph, basic blocks or
loops~\cite{Aho2006} that limit usage of assembly code to a few hot spots.
Language extensions like OpenMP~\cite{openmp4} provide a convenient parallel
programming model and libraries like Boost.SIMD~\cite{esterie2012boost} provide 
good abstractions for explicit vectorization. Many highly tuned kernels are
available in the form of thid-party libraies like GotoBlas~\cite{gotoblas2008}.

@@

% The first one holds 8 AMD Magny Cours processors for a
% total of 48 cores. Each core has access to 64\,KB of L1 cache,
% 512\,KB of L2 cache. Both L1 and L2 caches are private, while L3 cache
% is shared between the 6 cores of a processor. This configuration
% provides a total of 256\,GB (32\,GB per NUMA node) of main memory. It supports
% up to SSE4. We
% will refer to this configuration as \textbf{AMD48}.
% On AMD48, backend compilers are gcc (Debian 4.7.2-5) and the clang-omp version
% from intel~\footnote{\url{http://clang-omp.github.io/}} to be able to benefits
% from OpenMP improvement. This clang version is based on clang 3.4 release
% (LLVM:233b1e3f034, clang-omp:6f358bcd87).

% The second one holds 8 Intel(R) Xeon(R) CPU E5-2650 0 @ 2.00GHz for a ttal of
% 8 cores (multithreading is not used). Each node can access to  64\,KB of L1 cache,
% 256\,KB of L2 cache. Both L1 and L2 caches are private, while L3 cache
% is shared between the 8 processors. This configuration
% provides a total of 63\,GB of main memory. It supports up to AVX. We will
% refer to this configuration as \textbf{Intel8}.
% On Intel8, backend compilers are gcc 4.9 (20140528) and the clang-omp version
% from intel.
